### 2019-11-08 Action letter.Rmd
Contrasts in table

@@

Therefore, to address this comment, we have re-run all analyses to obtain the posterior for the differences between mothers and fathers. We have reported this information in-text whenever making a statement about mother/father differences, and have added it to the relevant Supplementary Tables with the full model parameters. We have omitted it from the smaller Tables in the manuscript, because their function is to help make it easier for readers to digest the results, and we feel that adding four columns with difference tests would interfere with that goal.

@@

>>>>

With regard to the Editorial Office's request that we upload a Word or RTF file: In line with the Submission Guidelines on the Developmental Psychology website, we have provided \latex as a `zip`-file, with accompanying `.pdf`. We do not have a Word version of this manuscript available.

@@

Therefore, to address this comment, we have re-run all analyses to obtain the posterior for the differences between corresponding parent- and child effects. We have explained this procedure in the text (fragment cited below), and have added it to Table 2 in the form of labels that indicate which parameters differed significantly, and we have reported the full difference tests in Supplementary Table S5.

<!--The interpretation of the difference tests is straightforward, because they exactly mirror the pattern of significant/non-significant parent and child effects: All effects that are significant in one direction, but non-significant in the reverse direction, have significant difference tests. All effects that are significant in both directions, or non-significant in both directions, have non-significant difference tests. It is therefore justifiable to simply interpret the pattern of significant parent- and child effects.

Section in Results:

> We established direction of effects by testing the significance of the difference between corresponding parent- and child effects (see Table \@ref(tab:tabcrosspath) and Supplementary Table S5). All effects that were significant in one direction, and non-significant in the opposite direction, had significant difference tests. All effects that were significant (or non-significant) in both directions had non-significant difference tests.

Table note:

> Matching letters indicate that parameters differed significantly, see Supplementary Table S5.-->

@@

Therefore, to address this comment, we have re-run all analyses to obtain the posterior for the differences between corresponding parent- and child effects. We have explained this procedure in the text (fragment cited below), and have added it to Table 2 in the form of labels that indicate which parameters differed significantly, and we have reported the full difference tests in Supplementary Table S5.

The interpretation of the difference tests is straightforward, because they exactly mirror the pattern of significant/non-significant parent and child effects: All effects that are significant in one direction, but non-significant in the reverse direction, have significant difference tests. All effects that are significant in both directions, or non-significant in both directions, have non-significant difference tests. It is therefore justifiable to simply interpret the pattern of significant parent- and child effects.

Section in Results:

> We established direction of effects by testing the significance of the difference between corresponding parent- and child effects (see Table \@ref(tab:tabcrosspath) and Supplementary Table S5). All effects that were significant in one direction, and non-significant in the opposite direction, had significant difference tests. All effects that were significant (or non-significant) in both directions had non-significant difference tests.

Table note:

> Matching letters indicate that parameters differed significantly, see Supplementary Table S5.

### 2019-11-08 Paper_shortened_pdf.Rmd
Contrasts in table

At the within-family level, we examined over-time cross-lagged effects between qualitative parenting and emotional adjustment. The intercepts of these random effects reflect the average cross-lagged effect across families. Their variances indicate whether the effect differs in strength (and sign) between families.

With regard to within-families parenting effects, none of the intercepts differed significantly from zero, excepting the effect of maternal warmth on children's emotional adjustment (Table \@ref(tab:tabcrosspath)). Thus, on average, mothers' warmth had a positive significant predictive effect on children's emotional adjustment. The variances of all parenting effects were all significant, however, indicating that the effect of qualitative parenting behaviors on children's emotional adjustment varies across families. Moreover, these variances were notably larger for fathers than for mothers, indicating that fathers have a more variable effect on their children through specific parenting behaviors than mothers do.

@@

tabchildeff$Parameter <- gsub("^\\((.+) on.*$", "\\1", tabchildeff$Parameter)
tabchildeff$Parameter[c(1,4)] <- c("Random intercepts of child effects on:", "Variance of child effects on:")
tab <- rbind(tabparenteff, tabchildeff)
#tab[is.na(tab)] <- ""
rownames(tab) <- NULL
tab$Parameter <- gsub("^Variance", "Unstandardized variance", tab$Parameter)
reg_table(tab, caption = "Standardized between-family level intercepts and unstandardized variances of within-family predictive effects", note = "Est.: Estimate. HDPI: Highest posterior density interval. Emo.: Emotional adjustment. *: <5% of posterior has opposite sign from estimate.")
```

@@

>>>>

At the within-family level, we examined over-time predictive effects between qualitative parenting and emotional adjustment. The intercepts of these random effects reflect the average effect across families. Their variances indicate whether the effect differs in strength (and sign) between families. With regard to within-families parenting effects, none of the intercepts differed significantly from zero, excepting the effect of maternal warmth on children's emotional adjustment (Table \@ref(tab:tabcrosspath)). Thus, on average, mothers' warmth had a positive significant predictive effect on children's emotional adjustment. The variances of all parenting effects were all significant, however, indicating that the effect of qualitative parenting behaviors on children's emotional adjustment varies across families. Moreover, these variances were notably larger for fathers than for mothers, indicating that fathers have a more variable effect on their children through specific parenting behaviors than mothers do.

@@

tabchildeff$Parameter <- gsub("^\\((.+) on.*$", "\\1", tabchildeff$Parameter)
tabchildeff$Parameter[c(1,4)] <- c("Random intercepts of child effects on:", "Variance of child effects on:")
tab <- rbind(tabparenteff, tabchildeff)
#tab[is.na(tab)] <- ""
rownames(tab) <- NULL

# Add letters for contrast tests

stars <- tab_unst_sections$`Defined parameters`[tab_unst_sections$`Defined parameters`$Parameter %in% c("Mother effect - child effect on mother", "Father effect - child effect on father"), ]
letter <- 1
tabrows <- list(c(2,8),
                c(3, 9))

for(i in 1:length(tabrows)){
  if(any(grepl("\\*", stars[i, ]))){
    for(c in which(grepl("\\*", stars[i, ]))){
      # c = 6
      tab[tabrows[[i]], c] <- paste0(tab[tabrows[[i]], c], letters[letter])
      letter <<- letter + 1
    }
  }
}

tab$Parameter <- gsub("^Variance", "Unstandardized variance", tab$Parameter)
reg_table(tab, caption = "Standardized between-family level intercepts and unstandardized variances of within-family predictive effects", note = "Est.: Estimate. HDPI: Highest posterior density interval. Emo.: Emotional adjustment. *: <5% of posterior has opposite sign from estimate. Matching letters indicate that parameters differed significantly, see Supplementary Table S5.")
```

@@

We established direction of effects by testing the significance of the difference between corresponding parent- and child effects (see Table \@ref(tab:tabcrosspath) and Supplementary Table S5). All effects that were significant in one direction, and non-significant in the opposite direction, had significant difference tests. All effects that were significant (or non-significant) in both directions had non-significant difference tests.

We examined differences between fathers and mothers the same way. <!-- NOG DOEN -->
